\section{Original Proposal}

\begin{itemize}
\item Monday 23/04/2018, 16:00: \\
Milestone: Deadline for submission of project specifications.
Requirements:
Outline of further project milestones.

\item Tuesday 24/04/2018 (13:15-15:00, room 1311): \\
Milestone: First feedback session on projects (individual groups).
Requirements:
Each member of the group has read the paper “Group-level Arousal and Valence Recognition in Static Images: Face, Body and Context.”

\item Friday 27/04/2018, 16:00: \\
Milestone: Deadline for submission of project specifications supplementation.
Requirements
List milestones in a per week basis.
Include details on how we plan to implement the data analysis, feature extraction, and classification tasks.

\item Wednesday 02/05/2018, 17:00: \\
Milestone: Analysis of dataset.
Requirements
Study data features and labels.
Perform a simple analysis on class imbalance and distribution of values (take notes on findings).
Be able to read in facial landmark positions as input from dataset.
Implement at least 2 different dimensionality reduction strategies (take notes on how each of them work and what does each hyperparameter do). Explore other methods of dimensionality reduction, optionally implement them.

\item Friday 04/05/2018, 17:00: \\
Milestone: Implement KNN and SVM models.
Requirements
Implement the two classifiers demonstrated in assignment 1 part 1 and get an accuracy higher than chance probability (take notes on the implementation, how each of the models work, on how does each hyperparameter affect the result, are there documented hyperparameters which could improve the results?)
Compare the two classifiers using the same methods as in assignment 1 part 1 and write notes on the obtained results.

\item Tuesday 08/05/2018 (13:15-15:00, room 1311): \\
Milestone: Second feedback session on projects (plenary).
Requirements:
Present progress of the implementation of the previous milestones in a coherent way.
Be able to read in facial landmark positions as input from Computer Vision group.
Classification results should be formatted such that they can be used by the Emotion Synthesis group.

\item Friday 11/05/2018, 17:00: \\
Milestone: Implement two more classifiers.
Requirements:
Implement two more classifiers different from the ones used in assignment 1 part 1 (take notes on the implementation, how each of the models work, on how does each hyperparameter affect the results).
Determine which of the four classifiers implemented gives the best result and research why is that the case.

\item Wednesday 16/05/2018, 17:00: \\
Milestone: Write down experiment and research notes in report format.
Requirements:
Report:
Write down report introduction.
State contributions.
Extend data analysis notes and write them down in the report.
Extend model implementation notes (including hyperparameter experiments) and write them down in the report.

\item Friday 18/05/2018, 17:00: \\
Milestone: Continue work on report.
Requirements:
Report:
Evaluate performance of each implemented model.
Discuss any further improvements that are applicable to our research.
Elaborate on potential ethical concerns we have identified with the emotional responsive agent.
Write down conclusions.

\item Monday 21/05/2018 (10:15-12:00, room 1311): \\
Milestone: Third feedback session on projects (individual groups).
Requirements:
Record a video showing a demo of the system developed during the project.

\item Wednesday 30/05/2018 (10:15-12:00, room 1311): \\
Milestone: Final project presentations by students.
Requirements:
Presentation which showcases how we have solved the problem and the obtained results.

\item Friday 01/06/2018, 16:00: \\
Milestone: Deadline for submission of projects’ reports and material.
Requirements:
Submit report (which should already be done by this point).
\end{itemize}
